Figures to insert in text

### 2018-03-16 Chapters/Chapter03.tex
Bass model: minor grammar and typo fixes

In this work, I propose an extension to the Bass model which (i) includes the negative effect of the rejections, (ii) is as simple as the \citet{bass1969} model, and (iii) its parameters can be estimated using the number of people who have adopted and have not posteriorly rejected the innovation, i.e., the number of \textit{active adopters}. An important difference between the number of \textit{active adopters} and the \textit{total adopters} is that first may decrease over time, while the latter cannot. First, I discuss the \citet{bass1969} model and its parameters; then I describe the model extension and analyze four models of rejection; next I detail the estimation method; after that I estimate the models by using Facebook's active users dataset; and finally, I discuss the results and conclude.

The main contribution of this work is that the proposed extension is the first to include the effect of the rejections that can be estimated using the number of \textit{active adopters} instead of the number of \textit{total adopters}. The model can be applied to forecast the number of active adopters of these companies in the next quarters, which becomes an important tool for analysts, investors, and the companies themselves. As the number of active adopters is related to the market cap of these companies, these forecasts may be useful to estimate the future value of the firms. At the time of this writing, Facebook's market cap is \$222.69B, Twitter's is \$23.18B, and Netflix's is \$20.49B\footnote{Data obtained from Yahoo! Finance website at December 1\textsuperscript{st}, 2016.}.

@@

The potential market size $m$ is the unknown number of people who will have adopted the innovation after a very long time. It is not exactly the target market of the innovation, but a subset of it, as no product difuses over its entire target market. If a company estimates and updates the model more than once for their product, the change in $m$ is a change in the potential market and could help the company to understand whether their decisions in the meantime have increased or decreased the number of future adopters. As, $\lim_{t \rightarrow \infty} Y(t) = m$, the whole potential market will have adopted the innovation at some point.

@@

These four models can be grouped in two families, one for the equations \ref{eq:model1} and \ref{eq:model2}, and another for the equations \ref{eq:model3} and \ref{eq:model4}. The former relates the rejection to the rate of new people adopting the innovation, as if people decide whether they will use or reject the innovation when they try it. Then, they do not change their position anymore. The latter assumption relates the rejection to the number of \textit{active users}, as if the \textit{active users} first adopt the innovation and then they continuously reject it.

@@

The right side of the differential equation \ref{eq:model2} is the rate of rejection, i.e., the probability of someone who rejecting the innovation, provided that he/she has not rejected it yet. Thus, in this model, the rate of rejection is proportional to the percentage of people adopting the innovation at time $t$, i.e., the more people adopt the innovation, the more they reject it. But if no one is adopting, there would be no rejection also, which would hold the number of \textit{active users} the same.

The differential equation \ref{eq:model2} can also be solved for $R(t)$ algebrically. Using the fact that $-\frac{d}{dt} \log[1 - R(t)] = r(t) / [1 - R(t)] = \nu f(t)$, and integrating both sides of this equation yields:

@@

In this model, the rate of new \textit{inactive users} increases linearly with the number of \textit{active users}, since $A(t) = F(t) - R(t)$. Thus, while there are \textit{active users}, a fraction $\nu$ of them will be rejecting the innovation. Hence, everyone will have reject the innovation sooner or later.

@@

In this model, the rate of rejection increases linearly with the number of \textit{active users}. Thus, while there are \textit{active users}, the rate of rejection will be greater than zero. Hence, everyone will have reject the innovation sooner or later.

@@

The parameters of the model should be estimated using empirical data in order to check the explanation power of the model. \citet{bass1969} used a discrete version of his differential equation with ordinary least squares. While it worked well for him, it has not in the present work. There are several well known problems in the estimation of parameters, most of them related to approximation of derivatives and instability of the estimators. These problems have been noticed by many authors \citep{schmittlein1982maximum, srinivasan1986technical, xie1997kalman}.

@@

Since there is no explicit solution for the parameters $m$, $p$, $q$, $w$, and $\nu$ which maximize the LogLikelihood function, the parameters were estimated using the Truncated Newton Constrained (TNC) method \citep{dembo1983truncated, nash2000survey, nash1984newton} from the SciPy Python Library \citep{scipy}. The constrains were $m > 0$, $p > 0$, $q > 0$, $w \geq 0$, and $\nu \geq 0$ for all models. The initial guess for the TNC method was the same for all models estimation. Sometimes, the method did not converge and another initial guess had to be used.

@@

The models parameters were estimated using the number of Facebook's \textit{active users} from December 2004 to March 2013 \citep{facebookdata}. In the dataset, $x_i$ was the number of Facebook's \textit{active users} at time $t_i$. The dataset had 23 non-equally time spaced measures. The users who have accessed Facebook at least once in each month were counted in the number of \textit{active users} in that month.

@@

It is also intended to run a back test with the available data. First, the parameters of the model is estimated using a subset of the dataset. Then, through extrapolation, the number of \textit{active uses} is forecast. Finally, it is compared to this part of the dataset - which must not have been used in the estimation.

>>>>

In this work, I propose an extension to the Bass model which (i) includes the negative effect of the rejections, (ii) is as simple as the \citet{bass1969} model, and (iii) its parameters can be estimated using the number of people who have adopted and have not posteriorly rejected the innovation, i.e., the number of \textit{active adopters}. An important difference between the number of \textit{active adopters} and the \textit{total adopters} is that first may decrease over time, while the latter cannot. First, I discuss the \citet{bass1969} model and its parameters; then I describe the model extension and analyze four models of rejection; next, I detail the estimation method; after that, I estimate the models by using Facebook's active users dataset; and finally, I discuss the results and conclude.

The main contribution of this work is that the proposed extension is the first to include the effect of the rejections that can be estimated using the number of \textit{active adopters} instead of the number of \textit{total adopters}. The model can be applied to forecast the number of active adopters of these companies in the next quarters, which becomes an important tool for analysts, investors, and the companies themselves. As the number of active adopters is related to the market cap of these companies, these forecasts may be useful to estimate the future value of the firms. At the time of this writing, Facebook's market cap is \$222.69B, Twitter's is \$23.18B, and Netflix's is \$20.49B\footnote{Data obtained from Yahoo! Finance website on December 1\textsuperscript{st}, 2016.}.

@@

The potential market size $m$ is the unknown number of people who will have adopted the innovation after a very long time. It is not exactly the target market of the innovation, but a subset of it, as no product diffuses over its entire target market. If a company estimates and updates the model more than once for their product, the change in $m$ is a change in the potential market and could help the company to understand whether their decisions in the meantime have increased or decreased the number of future adopters. As $\lim_{t \rightarrow \infty} Y(t) = m$, the whole potential market will have adopted the innovation at some point.

@@

These four models can be grouped into two families, one for the equations \ref{eq:model1} and \ref{eq:model2}, and another for the equations \ref{eq:model3} and \ref{eq:model4}. The former relates the rejection to the rate of new people adopting the innovation, as if people decide whether they will use or reject the innovation when they try it. Then, they do not change their position anymore. The latter assumption relates the rejection to the number of \textit{active users}, as if the \textit{active users} first adopt the innovation and then they continuously reject it.

@@

The right side of the differential equation \ref{eq:model2} is the rate of rejection, i.e., the probability of someone rejecting the innovation, provided that he/she has not rejected it yet. Thus, in this model, the rate of rejection is proportional to the percentage of people adopting the innovation at time $t$, i.e., the more people adopt the innovation, the more they reject it. But if no one is adopting, there would be no rejection also, which would hold the number of \textit{active users} the same.

The differential equation \ref{eq:model2} can also be solved for $R(t)$ algebraically. Using the fact that $-\frac{d}{dt} \log[1 - R(t)] = r(t) / [1 - R(t)] = \nu f(t)$, and integrating both sides of this equation yields:

@@

In this model, the rate of new \textit{inactive users} increases linearly with the number of \textit{active users}, since $A(t) = F(t) - R(t)$. Thus, while there are \textit{active users}, a fraction $\nu$ of them will be rejecting the innovation. Hence, everyone will have rejected the innovation sooner or later.

@@

In this model, the rate of rejection increases linearly with the number of \textit{active users}. Thus, while there are \textit{active users}, the rate of rejection will be greater than zero. Hence, everyone will have rejected the innovation sooner or later.

@@

The parameters of the model should be estimated using empirical data in order to check the explanation power of the model. \citet{bass1969} used a discrete version of his differential equation with ordinary least squares. While it worked well for him, it has not in the present work. There are several well-known problems in the estimation of parameters, most of them related to approximation of derivatives and instability of the estimators. These problems have been noticed by many authors \citep{schmittlein1982maximum, srinivasan1986technical, xie1997kalman}.

@@

Since there is no explicit solution for the parameters $m$, $p$, $q$, $w$, and $\nu$ which maximize the LogLikelihood function, the parameters were estimated using the Truncated Newton Constrained (TNC) method \citep{dembo1983truncated, nash2000survey, nash1984newton} from the SciPy Python Library \citep{scipy}. The constraints were $m > 0$, $p > 0$, $q > 0$, $w \geq 0$, and $\nu \geq 0$ for all models. The initial guess for the TNC method was the same for all models estimation. Sometimes, the method did not converge and another initial guess had to be used.

@@

The models' parameters were estimated using the number of Facebook's \textit{active users} from December 2004 to March 2013 \citep{facebookdata}. In the dataset, $x_i$ was the number of Facebook's \textit{active users} at time $t_i$. The dataset had 23 non-equally time spaced measures. The users who have accessed Facebook at least once in each month were counted in the number of \textit{active users} in that month.

@@

It is also intended to run a backtest with the available data. First, the parameters of the model are estimated using a subset of the dataset. Then, through extrapolation, the number of \textit{active users} is forecast. Finally, it is compared to this part of the dataset - which must not have been used in the estimation.
